\documentclass[11pt,british]{article}

\include{preamble}

\title{\textbf{CS2103T} \\ Team Project: CookBuddy}
\author{Sharadh Rajaraman \\ \textbf{A0189906L}}
\begin{document}
\maketitle

\section{Overview}\label{overview}

\href{}{} is a desktop recipe manager for students living in
on-campus accommodation, and who enjoy cooking, and are also familiar
with the command line.

Users may interact with CookBuddy through a Command Line Interface
(CLI), and it has a Graphical User Interface (GUI) created with JavaFX.

CookBuddy is written in Java, and has about \num{10000} lines of code.

\section{Summary of contributions}\label{summaryofcontributions}

\begin{itemize}
    \item
    \textbf{Major enhancement}: added \textbf{Image reading, processing and writing}.
    \begin{itemize}
        \item \textbf{What it does:} Allows users to add images to their recipes, by specifying a relative or absolute
        filepath. Images are saved in a data folder local to CookBuddy, and are named with a
        UID (unique identifier). If an image cannot be found at the specified path, a placeholder is used instead.
        \item
        Justification: Users should be able to see what the final dish looks
        like, and an image goes a very long way in showing that. Furthermore, images are a prominent feature of most
        competing recipe managers, and this is a key feature that should have been implemented.
        \item
        Highlights: This enhancement affects existing commands and commands
        to be added in future. It required an in-depth analysis of design
        alternatives. The implementation too was challenging as it required
        changes to existing commands.
        \item
        Credits: \emph{\{mention here if you reused any code/ideas from
            elsewhere or if a third-party library is heavily used in the feature
            so that a reader can make a more accurate judgement of how much
            effort went into the feature\}}
    \end{itemize}
    \item
    \textbf{Minor enhancement}: added a history command that allows the
    user to navigate to previous commands using up/down keys.
    \item
    \textbf{Code contributed}:
    \item
    \textbf{Other contributions}:
    \begin{itemize}
        \item
        Project management:

        \begin{itemize}
            \item
            Managed releases \texttt{v1.3} - \texttt{v1.5rc} (3 releases) on
            GitHub
        \end{itemize}
        \item
        Enhancements to existing features:
        \item
        Documentation:

        \begin{itemize}
            \item
            Did cosmetic tweaks to existing contents of the User Guide:
        \end{itemize}
        \item
        Community:

        \begin{itemize}
            \item
            PRs reviewed (with non-trivial review comments)
        \end{itemize}
        \item
        Tools:

        \begin{itemize}
            \item
            Integrated a third party library (Natty) to the project
            \item
            Integrated a new Github plugin (CircleCI) to the team repo
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{document}
